The \dealii{} Library, Version 9.3

### 2021-05-08 9.3/paper.tex
Fix a typo.
Update contributors

\subsection{MPI-3.0 shared-memory support}
In many large computations, certain pieces of data are computed once
and then threated as read-only. If this information is needed by more
than one MPI process, it is more efficient to store this information only
once in shared memory among all processes located on a multicore
node. MPI supports the creation of such shared memory windows since
version 3.0, and deal.II can now use this in the
\texttt{AlignedVector} and \texttt{Table} classes that are often used
for large lookup tables.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.2: updated 5/11/2020 MM
TODO

>>>>

\subsection{MPI-3.0 shared-memory support}
In many large computations, certain pieces of data are computed once
and then treated as read-only. If this information is needed by more
than one MPI process, it is more efficient to store this information only
once in shared memory among all processes located on a multicore
node. MPI supports the creation of such shared memory windows since
version 3.0, and deal.II can now use this in the
\texttt{AlignedVector} and \texttt{Table} classes that are often used
for large lookup tables.

@@

\dealii{} is a world-wide project with dozens of contributors around the
globe. Other than the authors of this paper, the following people
contributed code to this release:\\
%
% Uwe Koecher doesn't usually show up in the changelog, but
% we should make sure he's listed.
%
% 9.3: updated 5/08/2021 PM
Alexander Grayver,
Andrew Davis,
Arpit Babbar,
Bruno Blais,
Bruno Turcksin,
Ce Qin,
Christoph Kammer,
Conrad Clevenger,
Dominic Soldner,
Daniel Arndt,
Daniel Garcia-Sanchez,
Daniel Paukner,
David F. Castellanos,
David Wells,
Doug Shi-Dong,
David Schneider,
Elias Dejene,
Graham Harper,
Ignacio Tomas,
Ivan Fumagalli,
Jake Harmon,
Jean-Paul Pelteret,
Jiaqi Zhang,
Julian Roth,
Katharina Kormann,
Konrad Simon,
Krishnakumar Gopalakrishnan,
Laura Prieto Saavedra,
Lei Qiao,
Luca Heltai,
Magdalena Schreter,
Malhar Tidke,
Marc Fehling,
Marcus Calhoun-Lopez,
Martin Kronbichler ,
Mathias Anselmann,
Matthias Maier,
Maximilian Bergbauer,
Menno Fraters,
Michele Bucelli,
Nicola Giuliani,
Nicolas Barnafi,
Niklas Fehn,
Nils Much,
Olivier Guevremont,
Pasquale Africa,
Peter Munch,
Peter Westerbaan,
Phillip Mobley,
Pratik Nayak,
Praveen Chandrashekar,
Rene Gassmoeller,
Reza Rastak,
Richard Schussnig,
Sebastian Proell,
Simon Sticko,
Timo Heister,
Toni El Geitani Nehme,
Wenyu Lei,
Wolfgang Bangerth,
Zhou Lei
